\thesistitle

### 2019-06-30 sattose/paper.tex
Working on clone types and such

\subsection{Type 2 clones}\label{sec:type2}
Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.

@@

\subsubsection{Type 1R clones} \label{sec:type1r}
We propose an alternative definition of type 1 clones. This definition requires cloned fragments to be not just textually equal, but also functionally equal. Because of this, type 1R clones are a subset of type 1 clones. Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones).

@@

\subsubsection{Type 2R clones}\label{sec:type2r}
We tackle the previously outlined shortcomings of type 2R clones (see section We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored. Type 1R clones are a subset of type 2R clones. All rules that apply to type 1R clones also apply to type 2R clones. Additionally, type 2R clones allow variability in literals, variables and method calls. This variability however is constrained by a threshold. Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types. As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.

Type 2 clones allow any change in identifiers, literals, types, layout, and comments. For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones. Merging such clones can be harmful instead of helpful.

>>>>

\subsection{Type 2 clones}\label{sec:type2}
Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones. Merging such clones can be harmful instead of helpful.

@@

\subsubsection{Type 1R clones} \label{sec:type1r}
To solve the shortcomings listed in section \ref{sec:type1}, we propose an alternative definition of type 1 clones. This definition requires cloned fragments to be not just textually equal, but also functionally equal. Because of this, type 1R clones are a subset of type 1 clones. Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones).

@@

\subsubsection{Type 2R clones}\label{sec:type2r}
We tackle the previously outlined shortcomings of type 2R clones to be able to detect such clones that can and should be refactored. Type 1R clones are a subset of type 2R clones. All rules that apply to type 1R clones also apply to type 2R clones. Additionally, type 2R clones allow variability in literals, variables and method calls. This variability however is constrained by a threshold. Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types. As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.

### 2019-06-30 sections/research.tex
Working on clone types and such

\textbf{Type 1R:} Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that \
contains the code of both locations.
\textbf{Type 2R:} Allows difference between cloned fragments in controlled features of a codebase. Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
\textbf{Type 3R:} Allows any difference. When refactored, this difference must be wrapped in a conditionally executed block, which entails a major tradeoff.

>>>>

\begin{itemize}
\item \textbf{Type 1R:} Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that contains the code of both locations. \\
\item \textbf{Type 2R:} Allows difference between cloned fragments in controlled features of a codebase. Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff. \\
\item \textbf{Type 3R:} Allows any difference. When refactored, this difference must be wrapped in a conditionally executed block, which entails a major tradeoff.
\end{itemize}

\begin{equation}\label{eq:typerelation}
\text{Cloned statements} = T1R \subseteq T2R \subseteq T3R
\end{equation}

\begin{equation}\label{eq:typerelation2}
\text{Cloned lines} = T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
\end{equation}
